A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
For the PCA-Linear regression (PCA-LinReg) reduced order model of the permeability field, all the work is done in the principal component spaces. This can be completed in two steps, which is exemplified for the 2D model thus:
\begin{enumerate}
  \item The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.

@@

\item The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$. From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained. The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.

\end{enumerate}

>>>>

\subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
For the PCA-Linear regression reduced order model (PCA-LinReg) of the permeability data, all work is performed in PCS. This can be conducted in two steps (for 2-D models), thus:
\begin{description}
  \item[Step 1:] The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.

@@

\item[Step 2:] The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$. From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained. The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.

\end{description}
